---
title: "Data Analysis"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: row
    vertical_layout: scroll
    horizontal_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(plotly)


# Dataset :"https://github.com/skathirmani/ctm-2019/blob/master/datasets/ipl.zip"

URL_dataIPL = "https://github.com/skathirmani/ctm-2019/blob/master/datasets/ipl.zip"


```

File  {.sidebar}
=========================


```{r}
fileInput("uf_matches", "Upload a Match File")

fileInput("uf_deliveries", "Upload a Deliveries File")


```

Assignment - Question
=========================

Column
------------------------------------------------------------------------------------

```{r}

text1 = paste("###  Week 7: Assessment – Data Visualization")
text2 = paste("Dataset :- https://github.com/skathirmani/ctm-2019/blob/master/datasets/ipl.zip")
```

```{r}
text3 = paste(" Using IPL data set, create a shiny application with the following analysis as individual tabs in a R Shiny application.")
```

```{r}
text4 = paste(" 1.In the first tab, create a summary view for all the seasons. Season wise report winning team, batsman with highest run 
  scorer and bowler with highest number of wickets.")

text5 = paste("2. In the second tab for single season summary. Create dropdown for selecting a single season and report team wise number of matches won, top run scorer, highest wicket taker")
  
text6 = paste("3. In the third tab, come up with interesting charts to analyze players performance across seasons. Add appropriate filters and ,
  make sure that you have   a #dropdown to select a team and a player.")
  
text7 = paste("4. In the fourth tab, come up with interesting charts to analyze team performance in single season. Add appropriate filters and  make sure that you have a #dropdown for selecting a season and team.")
  
text8 = paste("Optional: Try deploying your application in shiny server using free plans. Sign up and see the steps in this link http://www.shinyapps.io for deployment.")

t = paste( text1,text2,text3,text4,text5,text6,text7,text8)
t
```

File Uploaded
=========================

Row 1
----------------------------------------------------------------------------------------------------------
### File Content ( Matches )

```{r}

uiOutput("matches_cols")
```

```{r}
  tableOutput("dfm_Tables_cols")
```

### File Content ( Deliveries )

```{r}
uiOutput("deliveries_cols")

```

```{r}
  tableOutput("dfd_Table_cols")
```

Row 2
----------------------------------------------------------------------------------------------------------

### File uploaded - Matches

```{r , fig.height=2, fig.width=5}
  tableOutput("fdatam")
```


### File uploaded - Deliveries

```{r , fig.height=2, fig.width=5}
  tableOutput("fdatad")
```

Summary View
==========================

Row 1
---------------------------------------------------------------------------------------------------------

### Batsman with Highest Run Score

```{r}

valueBoxOutput("HighestRun")

```

### Bowler with Highest Wicket

```{r}

valueBoxOutput("HighestWicket")

```

Row 2
------------------------------------------------------------------------------------

### Season wise Winner 

```{r}
plotOutput("Season_Winner")
```

Row 3
------------------------------------------------------------------------------------

### List of Season wise Winner 

```{r}
tableOutput("All_Season_TeamWon")
```

Single Season Summary View
==========================

```{r}
uiOutput("Single_Season")
```

```{r}
#uiOutput("Season_TeamWon")
```

Row 1
------------------------------------------------------------------------------------

### Season Highest Runs

```{r}

valueBoxOutput("SeasonHighestRun")

```

### Season Batsman with Highest Runs

```{r}
valueBoxOutput("SeasonHighestRun_Batsman")
```


### Bowler with Highest Wicket

```{r}

valueBoxOutput("SeasonHighestWicket")

```

Row 2
------------------------------------------------------------------------------------

### Season Winning Teams Data

```{r}
tableOutput("SeasonWinnerT")
```

### Season - Winning Teams Report

```{r}
plotlyOutput("SeasonWinnerT_Plot")
```


Team and Player Performance Summary View
=========================================

```{r}
uiOutput("SelectedTeam")
```

```{r}
uiOutput("SelectedPlayer")
```

Row 1 
------------------------------------------------------------------------------------

### Team Batting Performance

```{r}
plotOutput("BattingTeam_Performance")
```

### Team Bowling Performance

```{r}
plotOutput("BowlingTeam_Performance")
```

Row 2
------------------------------------------------------------------------------------

### Player Batting Performance

```{r}
plotOutput("BattingTeam_Player_Performance")
```

### Player Bowling Performance

```{r}
plotOutput("BowlingTeam_Player_Performance")
```




```{r}

options(shiny.maxRequestSize = 40*1024^2)

observe({
  # File Upload
  if(is.null(input$uf_matches)){
    return(NULL)
  }
    output$fdatam = renderTable({
   input$uf_matches
  })
  
  if(is.null(input$uf_deliveries)){
    return(NULL)
  }
    output$fdatad = renderTable({
   input$uf_deliveries
  })
  
  dfmatches = read.csv(input$uf_matches$datapath,sep=,)
  cols_dfm = colnames(dfmatches)

  dfdeliveries = read.csv(input$uf_deliveries$datapath,sep=,)
  dfdeliveries$dfd_season = as.integer(strptime(as.Date(dfdeliveries$date,'%d-%m-%y'), '%Y')$year+1900 )
  cols_dfd = colnames(dfdeliveries)
  
  output$matches_cols = renderUI({
    selectInput( inputId = "dfm_col", label = "select a Matches Column", 
                 choices = cols_dfm, multiple = TRUE )
  })
  
  output$deliveries_cols = renderUI({
    selectInput( inputId = "dfd_col", label = "select a Delivery Column", 
                 choices = cols_dfd, multiple = TRUE )
  })
 
  output$dfm_Tables_cols = renderTable({
   dfmatches[1:10,input$dfm_col]
  })
  
  output$dfd_Table_cols = renderTable({
   dfdeliveries[1:10,input$dfd_col]
  })
  
  # Summary View
  
  output$HighestRun = renderValueBox({
    
    BatHigh = dfdeliveries %>% select(batsman,batsman_runs) %>% group_by(batsman) %>% 
      summarise(TotalRuns = sum(batsman_runs)) %>% 
      arrange(-TotalRuns) %>% top_n(1)
    BatHigh$batsman
  })
  
  output$HighestWicket = renderValueBox({
      
   wickets = dfdeliveries[dfdeliveries$player_dismissed !="",] %>% select(bowler,player_dismissed) %>% 
      group_by(bowler)%>% 
      summarise(unique(bowler,player_dismissed),w = n()) %>% 
      arrange(-w)%>% top_n(1)
      wickets$bowler
  })
  
  output$Season_Winner = renderPlot({
    
    dfmatches %>% select(season, winner) %>% group_by(season,winner) %>% summarise(season, winner, Wins = n()) %>%
      ggplot(aes(x=season,y=Wins,color=winner)) +
      geom_line(stat='identity', na.rm=F) +
      geom_point(size=4)
    
  })
  
  output$All_Season_TeamWon = renderTable({
      
   Season_Team_Win = dfmatches %>% 
      select(season,winner) %>% 
      group_by(season,winner) %>% 
      filter(winner!="")%>%
      summarise(won = n()) %>% 
      arrange(season)
  })
  
  # Single Season Summary View
 
  select_season = sort(as.integer(unique(dfdeliveries$dfd_season)))
  
  output$Single_Season = renderUI({
    selectInput( inputId = "dseason", label = "select a season", 
                 choices = select_season, multiple = FALSE)
  })

  #Season Highest Run & Batsman
  SHRTemp = dfdeliveries %>% select(dfd_season,batsman,batsman_runs) %>% filter(dfd_season %in% input$dseason)
  
  SHighestRun = SHRTemp %>% group_by(batsman) %>% 
      summarise(total_runs=sum(batsman_runs,na.rm=T)) %>% 
      arrange( -total_runs) %>% top_n(1)
   SH_run = SHighestRun$total_runs
   SH_batsman = SHighestRun$batsman
 
  output$SeasonHighestRun = renderValueBox({
      SH_run
  })
  output$SeasonHighestRun_Batsman = renderValueBox({
      SH_batsman
  })
  
  #Season Bowler with Highest Wicket Score
  output$SeasonHighestWicket = renderValueBox({
      
      wickets = dfdeliveries[dfdeliveries$player_dismissed !="",] %>% 
        select(dfd_season,bowler,player_dismissed) %>% 
        group_by(bowler)%>% 
        filter(dfd_season == input$dseason) %>%
        summarise(unique(bowler,player_dismissed),w = n()) %>% 
        arrange(-w)%>% top_n(1)
        ifelse(!is.null( wickets$bowler),wickets$bowler,"NA")
  })
  
  output$SeasonWinnerT = renderTable({
      
        SWTeam = dfmatches %>% 
        select(season,winner) %>% 
        filter( season == input$dseason , winner != "")%>%
        group_by(winner) %>% 
        summarise( WinnerTeam = unique(winner), won = n()) %>% 
        arrange(-won)
        SWTeam
     
  })
  output$SeasonWinnerT_Plot = renderPlotly({
      
        SWTeam = dfmatches %>% 
        select(season,winner) %>% 
        filter( season == input$dseason , winner != "")%>%
        group_by(winner) %>% 
        summarise( WinnerTeam = unique(winner), won = n()) %>% 
        arrange(-won) %>% 
          ggplot(aes(x=WinnerTeam,y=won),color='steelblue') + 
          geom_bar(stat='identity',na.rm=T) +
          labs(title = " Season Winner Teams with No of Matches Won", x = " Teams ", y = " No. of Wins ")+
           theme(axis.text.x = element_text(angle = 45))
          
        ggplotly(SWTeam)
     
  })
  
  select_teams <- unique( c(dfmatches$team1,dfmatches$team2) ) 
  select_player <- unique(c(dfdeliveries$batsman,dfdeliveries$bowler,dfdeliveries$fielder))
  
  output$SelectedTeam = renderUI({
    selectInput( inputId = "dteam", label = "Select Team", 
                 choices = select_teams, multiple = FALSE)
  })
    
  output$SelectedPlayer = renderUI({
    selectInput( inputId = "dplayer", label = "Select Player", 
                 choices = select_player, multiple = FALSE)
  })
  
  
  
    
  output$BattingTeam_Performance = renderPlot({
    
    battingteamplot = dfdeliveries %>% 
      select(match_id,dfd_season,batting_team,batsman,bye_runs,legbye_runs,penalty_runs,extra_runs,total_runs)%>%
      filter(batting_team == input$dteam) %>%
      group_by(dfd_season,batting_team)%>%
      summarise(Yrs=unique(dfd_season),Batting=unique(batsman),ByeRun=sum(bye_runs),LegBye = sum(legbye_runs),Penalities = sum(penalty_runs),Extra = sum(extra_runs),TotalRuns=sum(total_runs),TotalMatches=n()) %>% 
        arrange(dfd_season,Batting,-TotalMatches)
      
      battingteamplot %>% ggplot(aes(x=Batting, y=TotalRuns,colors=Batting))+
        geom_bar(stat='identity',na.rm=T) +
        facet_wrap(~Yrs )
  }) 
  
  output$BowlingTeam_Performance = renderPlot({
    bowlingteamdetails = dfdeliveries %>% 
      select(match_id,dfd_season,bowler,match_id,bowling_team,wide_runs,penalty_runs,extra_runs,non_striker,player_dismissed,over)%>%
      filter(bowling_team == input$dteam) %>%
      group_by(dfd_season,bowler)%>%
      summarise(Bowlers=unique(bowler),Yrs=unique(dfd_season),TotalMatches=n(),Wide=sum(wide_runs),Penarly=sum(penalty_runs),Extra=sum(extra_runs), Overs = sum(over)) %>%
      arrange(dfd_season,-TotalMatches) 
      
     ggplot(bowlingteamdetails,aes(x=Bowlers, y=Overs,colors=Bowlers))+
        geom_bar(stat='identity',na.rm=T) +
        facet_wrap(~Yrs )
  })
  

    output$BattingTeam_Player_Performance = renderPlot({
    
    battingteamplot = dfdeliveries %>% 
      select(match_id,dfd_season,batting_team,batsman,bye_runs,legbye_runs,penalty_runs,extra_runs,total_runs)%>%
      filter(batsman == input$dplayer) %>%
      group_by(dfd_season,batting_team)%>%
      summarise(Yrs=unique(dfd_season),ByeRun=sum(bye_runs),LegBye = sum(legbye_runs),Penalities = sum(penalty_runs),Extra = sum(extra_runs),TotalRuns=sum(total_runs),TotalMatches=n()) %>% 
        arrange(dfd_season,-TotalMatches)
      
      battingteamplot %>% ggplot(aes(x=Yrs, y=TotalRuns,colors=Yrs))+
        geom_bar(stat='identity',na.rm=T) +
        facet_wrap(~Yrs )
  }) 
  
  output$BowlingTeam_Player_Performance = renderPlot({
    bowlingteamdetails = dfdeliveries %>% 
      select(match_id,dfd_season,bowler,match_id,bowling_team,wide_runs,penalty_runs,extra_runs,non_striker,player_dismissed,over)%>%
      filter(bowler == input$dplayer) %>%
      group_by(dfd_season,bowler)%>%
      summarise(Yrs=unique(dfd_season),TotalMatches=n(),Wide=sum(wide_runs),Penalty=sum(penalty_runs),Extra=sum(extra_runs), Overs = sum(over)) %>%
      arrange(dfd_season,-TotalMatches) 
      
     ggplot(bowlingteamdetails,aes(x=Yrs, y=Overs,colors=Yrs))+
        geom_bar(stat='identity',na.rm=T) +
        facet_wrap(~Yrs )
  })
  
  
})
  
```