---
title: "Data Visualization : Assignment-Week1"
output: html_document
author: "Kapil K"
date: "July 18, 2020"
---

### Assessment 1 - Part 2
### Use the dataset from the link below and create appropriate visuals.
### https://github.com/skathirmani/ctm-2020/blob/master/datasets/us.car.accidents.csv.zip
## Question 1 :
### Using car accidents data set (available in the github repository, link is given above), identify the types of columns available

### Code : ( URL Download , Unzip not working )
```{r}
setwd("C:\\Users\\kushwaha\\Documents\\Kapil-Own\\CTM-IITM\\R-WorkSpace\\Week01")
getwd()
ms =read.csv("us.car.accidents.csv",sep=",")
names(ms)
print("\n\n")
sapply(ms, typeof)


```
## Question 2 :

### Using car accidents data sets identify the following
### 1. Identify how many different types of Race are available in the data set
### 2. For each Race, identify the number of accidents reported
### 3. Using Injury Severity column, identify percentage of Fatal Injury (K)

### Code : 

```{r}
library(dplyr)
RaceTyep <- select(ms,Race, Fatalities.in.crash ) %>% summarise(RaceTyep = unique(ms$Race))
print('Race Types of Races :')
print(RaceTyep)

df <- select(ms,Race, Fatalities.in.crash) %>% group_by(Race) %>% summarise(RaceTyep = unique(Race), Acc = sum(Fatalities.in.crash))
No_Accidents = select(df, RaceTyep, Acc)
print(No_Accidents)

Total_Fatalities <- sum(ms$Fatalities.in.crash)

df <- select(ms,Race, Fatalities.in.crash, Injury.Severity)%>%  group_by(Injury.Severity) %>% summarize(Injury = unique(Injury.Severity), Acc = sum(Fatalities.in.crash), Percent_Fatalities = round( (Acc/Total_Fatalities * 100),2))
 
Percent_F <- select(df, Injury , Percent_Fatalities)

print(Percent_F)

```
### Using the categorical columns in the cars data set create a data frame with the following columns
###  1 Column name
###  2 No. of unique levels
###  3 Most frequent level
###  4 Percentage of most frequent level
###  5 %Levels contribute to 80% frequency: Identify what percentage of levels are required to get 80% of the frequency

```{r}
library(dplyr)
Column_name <- names(ms)
Column_name = data.frame(Column_name)
print(Column_name)
#2 No. of unique levels
df <- data.frame(ms)

#2 No. of unique levels
Level_State  <- data.frame(unique(df$State) )	
Total_Count = nrow(Level_State)
print("No. of Unique Levels :" )
print(Total_Count )

#3 Most frequent level
dt <- select(ms,State, Race)%>%  group_by(State)   %>% summarize( Freq_State = n())
df <- select( dt,State,Freq_State)  %>% summarize( State,Frequent_State = (Freq_State/n()) ) %>% arrange(desc(Frequent_State))
print(df[1,1])


#4 Percentage of most frequent level
print( round(df[1,2],2) )
      

```


```{r}
#5 %Levels contribute to 80% frequency: Identify what percentage of levels are required to get 80% of the frequency
library(dplyr)
 
 
 cities <- c(ms$State, ms$Fatalities.in.crash)
 Uniq_Cities <- c(unique(ms$State))
 
 TotalF <-sum(ms$Fatalities.in.crash)
 
 T <- select(ms,State,Fatalities.in.crash)
 TF <- select(T,State, Fatalities.in.crash) %>% group_by(State)   %>% summarize( Total_Fatalities = (sum(Fatalities.in.crash)), PFatalities = (( Total_Fatalities/TotalF) *100)) %>% arrange( desc(PFatalities))
 Lfatal = max(TF$PFatalities)
 Lfatal

 PLevel = Lfatal*0.8
 PLevel
 P80cities <- select(TF,State, PFatalities) %>% group_by(State) %>% summarize( PFatalities, List_80 = (PFatalities > PLevel)) %>% filter(List_80==TRUE) %>% arrange(desc(PFatalities))
summary(P80cities )
summary(TF)
P80cities



```
