---
title: "Data Visualization : Assignment-Week03"
output: html_document
author: "Kapil K"
date : "August 02, 2020"
---

### Week 3: Assessment – Data Visualization



### Used knitr to set root dir 
#### root.dir = "C:\\Users\\kushwaha\\Documents\\Kapil-Own\\CTM-IITM\\R-WorkSpace\\Week03"

```{r setup, include=FALSE}

# Setting the working directory
knitr::opts_knit$set(root.dir = "C:\\Users\\kushwaha\\Documents\\Kapil-Own\\CTM-IITM\\R-WorkSpace\\Week03")

```
####
#### Using the waiter’s tip data set, perform the following
#### Q1. Calculate average tip by the following groups and visualize the same using bar charts
#### a. Gender
#### b. Size of the party
#### c. Smoker vs Non-Smoker
#### d. Day of the week
####  --- 
#### Data set link: https://github.com/skathirmani/datasets/blob/master/tips.csv

#### Data set description: Description for individual columns are listed below

#### total_bill: bill in dollars
#### tip: tip in dollars
#### sex: gender of the bill payer
#### smoker: whether there were smokers in the party
#### day: day of the week
#### time: time of day
#### size: size of the party

#### tips - dataset read from tips.csv

```{r , warning=FALSE, message=FALSE, fig.height=5,fig.width=10}

library(ggplot2)
library(dplyr)
library(plotly)

tips <- read.csv("tips.csv")
tips <- data.frame(tips)
```
#### Code for :
#### a. Gender
#### 
#### Variables Used : 
#### avg_tip_bygender - Average tip by Gender ( Day , Sex, Avg_tips ) #calculated by day 
#### tips - data frame of data read from tips.csv
#### Avg_tips - average tips per day for Gender or Sex
```{r, warning=FALSE, message=FALSE, fig.height=5,fig.width=10}

avg_tip_bygender <- select(tips,tip,sex,day) %>% 
                        group_by(day,sex) %>% 
                        summarise( Days= unique(day) , Gender = unique(sex), Avg_tips = mean(tip,na.rm=F) ) 

ggplot(avg_tip_bygender, aes(x=Days, y=Avg_tips,fill=Gender) ) +
  geom_bar(stat="Identity",na.rm = F)+
  labs(  title = ' Avg Tips by Gender - Day wise')

```

#### b. Size of the party
#### Size_of_Party - data for average tips as per size of party
#### Avg_tips - average tips per day for Gender or Sex

```{r, message = FALSE, warning=FALSE, fig.height=5,fig.width=10}

Size_of_Party <- select(tips,tip,size,day) %>% 
                        group_by(day,size) %>% 
                        summarise(  days = unique(day) , Party_Size = unique(size), Avg_tips = mean(tip,na.rm=F) ) 

ggplot(Size_of_Party, aes(x=days, y=Avg_tips )) +
  geom_bar(aes(x=days, y = Avg_tips, fill=Party_Size),stat = 'identity',na.rm = F)+
  geom_point(aes( size = Party_Size),color="orange") +
  geom_line( aes(group = Party_Size) )  +
  labs( x= "Days",  title = ' Avg Tips by Party Size - Day wise',hjust=2)+
  facet_wrap(~Party_Size)
  


```
#### c. Smoker vs Non-Smoker
#### Party_Smoker - data for average tips as per size of party
#### Avg_tips - average tips per day for Gender or Sex
```{r, message=FALSE, warning=FALSE}

Party_Smoker <- select(tips,tip,smoker,day) %>% 
                        group_by(day,smoker) %>% 
                        summarise(  days = unique(day) , smoke = smoker, Avg_tips = mean(tip,na.rm=F) ) 

ggplot(Party_Smoker, aes(x=smoke, y=Avg_tips,fill=smoke)) +
  geom_bar(stat='Identity')
  
  

```
#### d. Day of the week

```{r, message=FALSE, warning=FALSE}

Party_Days <- select(tips,tip,smoker,day) %>% 
                        group_by(day) %>% 
                        summarise(  days = unique(day), Avg_tips = mean(tip,na.rm=F) ) 

ggplot(Party_Days, aes(x=days, y=Avg_tips )) +
  geom_bar(aes(x=days, y = Avg_tips,fill=days),stat = 'identity',na.rm = F)+
  geom_point(aes( size = days), stat = "Identity") +
  geom_line( aes(group = 1) )  +
  labs( x= "Days",  title = ' Avg Tips by Day of the week') 

  

```





### Q2. Also create box plot for tip amount column. Split the box plot by above mentioned categories.

#### Code for 
#### a. Gender

```{r}

avg_tip_bygender <- select(tips,tip,sex,day) %>% 
                        group_by(day,sex) %>% 
                        summarise( Days= unique(day) , Gender = unique(sex), Avg_tips = mean(tip,na.rm=F) ) 

  ggplot(avg_tip_bygender, aes(x=Days, y=Avg_tips )) +
  geom_boxplot(aes(color=Gender,fill = Gender)) +
  labs(  title = ' Box Plot Avg Tips by Gender ') 


```


#### b. Size of the party
#### Size_of_Party - data for average tips as per size of party
#### Avg_tips - average tips per day for Gender or Sex

```{r, warning=FALSE,message=FALSE}
require(plotly)
Size_of_Party <- select(tips,tip,size,day) %>% 
                        group_by(day,size) %>% 
                        summarise(  days = unique(day) , Party_Size = unique(size), Avg_tips = mean(tip,na.rm=F) ) 

plt <- ggplot(Size_of_Party, aes(x=days, y=Avg_tips,fill=days)) + geom_boxplot() + 
  labs( x= "Days",  title = ' Avg Tips by Party Size - Day wise',hjust=2)+
  guides(fill=FALSE) + coord_flip()

fig <- ggplotly(plt)
fig
```

#### c. Smoker vs Non-Smoker

```{r, warning=FALSE,message=FALSE}
require(plotly)

Party_Smoker <- select(tips,tip,smoker,day) %>% 
                        group_by(day,smoker) %>% 
                        summarise(  days = unique(day) , smoke = smoker, Avg_tips = mean(tip,na.rm=F) ) 

plt <- ggplot(Party_Smoker, aes(x=days, y=Avg_tips)) +
  geom_boxplot(aes(  fill = smoke, color = smoke, size= Avg_tips)) +
  geom_line( aes(group=smoke) )  +
  labs( x= "Days",  title = ' Avg Tips by Smoker vs Non Smoker - Day wise')

fig <- ggplotly(plt)
fig

```

#### d. Day of the week

```{r, warning=FALSE,message=FALSE}

require(plotly)

Party_Days <- select(tips,tip,smoker,day) %>% 
                        group_by(day) %>% 
                        summarise(  days = unique(day), Avg_tips = mean(tip,na.rm=F) ) 

plt <- ggplot(Party_Days, aes(x=days, y=Avg_tips )) +
  geom_boxplot(aes(  fill = days, color = days, size = Avg_tips))+
  geom_point(color="darkblue") +
  geom_line( aes(group = 1 ), color="lightblue" )  +
  labs( x= "Days",  title = ' Avg Tips by Day of the week') 

fig <- ggplotly(plt)
fig
```
#### Q3. Using the above bar charts &amp; box plots, identify which group influences the tip amount.

```{r, warning=FALSE,message=FALSE}
require(plotly)
plt <- tips %>% ggplot(aes(x=total_bill, y=tip)) +geom_point() 

  fig <- ggplotly(plt)
fig

```
####
#### Q4. Visualize the relationship between total bill amount vs tip amount using scatter plot. The metric of interest should always be in the Y-axis. Here we are interested in understanding the tip pattern. Hence Y-axis should be tip amount and X axis should be total bill.
####

```{r,warning=FALSE,message=FALSE}
    require(plotly)
    plt <- tips %>% ggplot(aes(x=total_bill, y=tip, color=day)) + 
              geom_point() 
    
    fig <- ggplotly(plt)
    fig
    

```



####  Q5. Based on the above scatter plot, what do you think the waiter will do. Will he/she make you eat more or less to get good tip?
####  Q6. In the above scatter plot, color each circle by gender and list down your inferences

```{r,warning=FALSE,message=FALSE, fig.width=15,fig.height=5}
require(plotly)
names(tips)

total_tips = sum(tips$tip)
coparison <- select( tips, sex, total_bill, tip) %>% group_by(sex) %>% summarise(sex,Avg_tips=mean(tip, na.rm=F) ) 

ggplot(coparison, aes(x=sex,y=Avg_tips, color=sex)) +
  geom_point(size=5) +
  geom_smooth() +
  labs(caption = " Average Male tips are higher then Female to get good tips")



```
####